### 2023-04-11 chapter2/chapter2_supporting.tex
Added hierarchy rate figure to chapter 2 supplement

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy_histogram.png}
\centering
\caption{\textbf{Rate distributions of substitution models fit to disorder regions.}
\textbf{(A)} Average amino acid rates in regions. \textbf{(B)}. Average indel rates in regions. For both panels, the grey intervals correspond to the subset of rapidly evolving regions used for the clustering and GO term enrichment analyses.}
\label{sfig:hierarchy_histogram}
\end{figure}
